DraftOne

### 2016-09-14 writing/DraftOne.Rmd
fix examples in fit_models, delete rep_sims

>>>>

```{r}
#' Run simulations
#'
#' This function runs many simulations for a given dataset and model.
#'
#' @param n_sims A numeric value specifying the number of repetitions of the
#'    simulation to run
#' @param model A character string specifying which model to use.  Options
#'    include "spline_mod" and "casecross_mod"
#' @param n A numeric value specifying the number of days for which to simulate
#'    data
#' @param rr A numeric value specifying the relative risk for each 1-unit
#'    increase in exposure
#' @param x_type A character string specifying the type of exposure data.
#'    Options are "binary" and "continuous".
#' @inheritParams continuous_exposure
#' @inheritParams binary_exposure
#'
#' @return A data frame with the summaries of the estimate of the log relative
#'    risk for each simulation run
#'
#' @examples
#' rep_sims(n_sims = 3, model = "spline_mod")
#'
#' @export
#'
rep_sims <- function(n_sims, model, n = 5 * 365, rr = 1.01,
                     x_type = "continuous", mu = 10, sd = 2, lambda = 100){
  out <- replicate(n_sims, eval(call(model,
                                     sim_data(n = n, rr = rr,
                                              x_type = x_type,
                                              mu = mu, sd = sd,
                                              lambda = lambda))))
  out <- as.data.frame(t(out))
  names(out) <- c("est", "se", "t", "p", "lower_ci", "upper_ci")
  return(out)
}

```
